### 2015-06-10 paper/paper.Rmd
Proposed new verbiage for middle-eastern discussion

The countries are sorted from biggest gap to smallest gap. Most countries have a gender gap in math scores in favor of boys. Colombia has the biggest gender gap, about 30 points on average boys do better than girls. It should be noted that this is small, though, because this 30 points is out of a possible 1000 points.  Five countries have gender gaps in favor of girls, and even more surprising, these are middle eastern or Muslim countries.

>>>>

The countries are sorted from biggest gap to smallest gap. Most countries have a gender gap in math scores in favor of boys. Colombia has the biggest gender gap, about 30 points on average boys do better than girls. It should be noted that this is small, though, because this 30 points is out of a possible 1000 points.

Five countries have gender gaps in favor of girls; these are middle-eastern countries. Given popular perception of gender issues in the region, this may be a surprising result. Perhaps this is an example of how data can be used to show that reality is more nuanced than popular perception.
